### 2011-11-25 AffineLieAlgebras/Thesis/1.tex
More translation in chapter 1.

\begin{theorem}
  Для сингулярных коэффициентов ветвления $k^{(\mu)}_{\nu}$ (\ref{eq:21}) выполняется соотношение
  \begin{equation}
    \label{recurrent-relation}
    \begin{array}{c}
      k_{\xi }^{\left( \mu \right) }=-\frac{1}{s\left( \gamma _{0}\right) }\left(
        \sum_{u\in U} \epsilon(u)\;
        \dim \left( L_{\widetilde{\af_{\perp }}}^{\mu
        _{\widetilde{\af_{\perp }}}\left( u\right) }\right)
        \delta_{\xi-\gamma_0,\pi_{\af}(u(\mu+\rho)-\rho)}+ \right.\\
      \left.
        +\sum_{\gamma \in
          \Gamma _{\af \rightarrow \gf}}s\left( \gamma +\gamma _{0}\right) k_{\xi
          +\gamma }^{\left( \mu \right) }\right).
    \end{array}
  \end{equation}
\end{theorem}
\begin{proof}

Redress relation (\ref{eq:4}) for the element $
\frac{\Psi _{\gf}^{\mu }}{R_{\af_{\perp }}}$ using definition (\ref{eq:37})
for the carrier $\Phi _{\af\subset \gf}$ ,
\begin{equation*}
\begin{array}{l}
\Psi ^{\left( \mu \right) }_{\left(  \af, \afb \right)}
=\pi _{\af}\left( \frac{\Psi _{\gf}^{\mu }}{R_{\af_{\perp }}}%
\right) = \\[2mm]
=\prod\limits_{\alpha \in \Delta ^{+}\setminus \Delta _{\afb }^{+}}\left(
1-e^{-\pi _{\af}\alpha }\right) ^{\mathrm{mult}(\alpha )-\mathrm{mult}_{%
\af}(\pi _{\af}\alpha )}\left( \sum\limits_{\nu \in P_{\af%
}^{+}}b_{\nu }^{(\mu )}\sum\limits_{w\in W_{\af}}\epsilon (w)e^{w(\nu
+\rho _{\af})-\rho _{\af}}\right) = \\[5mm]
=-\sum\limits_{\gamma \in \Phi _{\af\subset \gf}}s(\gamma
)e^{-\gamma }\left( \sum\limits_{\nu \in P_{\af}^{+},w\in W_{\af%
}}\epsilon (w)b_{\nu }^{(\mu )}e^{w(\nu +\rho _{\af})-\rho _{\af%
}}\right)  \\
=-\sum\limits_{\gamma \in \Phi _{\af\subset \gf}}s(\gamma
)e^{-\gamma }\left( \sum\limits_{\nu \in P_{\af}^{+},w\in W_{\af%
}}\epsilon (w)b_{\nu }^{(\mu )}e^{w(\nu +\rho _{\af})-\rho _{\af%
}}\right) .
\end{array}
\end{equation*}

Then expand the sum in brackets (with respect to the formal basis in $\mathcal{E}$%
):
\begin{equation*}
\Psi ^{\left( \mu \right) }_{\left(  \af, \afb \right)}
=-\sum_{\gamma \in \Phi _{\af\subset \gf}}s(\gamma
)e^{-\gamma }\sum_{\lambda \in P_{\af}}k_{\nu }^{(\mu )}e^{\lambda
}=-\sum_{\gamma \in \Phi _{\af\subset \gf}}\sum_{\lambda \in P_{%
\af}}s(\gamma )k_{\nu }^{(\mu )}e^{\lambda -\gamma }.
\end{equation*}
Substitute the expression obtained in Lemma \ref{lemma} (in the left-hand side),
\begin{eqnarray*}
\Psi ^{\left( \mu \right) }_{\left(  \af, \afb \right)}
&=&\sum_{u\in U}\;\epsilon (u)e^{\pi _{\af}\left( \mu _{\frak{a%
}}\left( u\right) \right) }\dim \left( L_{\widetilde{\af_{\perp }}%
}^{\mu _{\widetilde{\af_{\perp }}}\left( u\right) }\right)
\label{anom modules 2} \\
&=&\sum_{u\in U}\;\epsilon (u)e^{\pi _{\af}\left[ u(\mu +\rho )-\rho %
\right] }\dim \left( L_{\widetilde{\af_{\perp }}}^{\mu _{\widetilde{%
\af_{\perp }}}\left( u\right) }\right)  \\
&=&-\sum_{\gamma \in \Phi _{\af\subset \gf}}\sum_{\lambda \in P_{%
\af}}s(\gamma )k_{\nu }^{(\mu )}e^{\lambda -\gamma }.
\end{eqnarray*}
The immediate consequence of this equality is:
\begin{equation}
\sum_{u\in U}\epsilon (u)\dim \left( L_{\widetilde{\af_{\perp }}}^{\mu
_{\widetilde{\af_{\perp }}}\left( u\right) }\right) \delta _{\xi ,\pi _{%
\af}\left[ u(\mu +\rho )-\rho \right] }+\sum_{\gamma \in \Phi _{\af%
\subset \gf}}s(\gamma )\;k_{\xi +\gamma }^{(\mu )}=0,\quad \xi \in P_{%
\af}.  \label{eq:17}
\end{equation}
The obtained formula means that the coefficients $k_{\xi +\gamma }^{(\mu )}$
for $\gamma \in \Phi _{\af\subset \gf}$ are not independent, they
are subject to linear relations and the form of these relations changes
when the tested weight $\xi $ coincides with one of \ the ''singular
weights''  $\left\{ \pi _{\af}\left[ u(\mu +\rho )-\rho \right] |u\in
U\right\} $ . To conclude the proof we extract the lowest weight $\gamma _{0}\in \Phi _{\frak{a%
}\subset \gf}$ and pass to a summation over the vectors of the
injection fan $\Gamma _{\af\rightarrow \gf}$ (see Definition \ref
{fan-definition}). Thus we get the desired recurrent relation (\ref{recurrent-relation}).
\end{proof}

\subsubsection{Embeddings and orthogonal pairs in simple Lie algebras}
\label{sect-embeddings}

>>>>

\begin{theorem}
  Для сингулярных коэффициентов ветвления $k^{(\mu)}_{\nu}$ (\ref{eq:21}) выполняется соотношение
  \begin{equation}
    \label{recurrent-relation}
    \begin{array}{c}
      k_{\xi }^{\left( \mu \right) }=-\frac{1}{s\left( \gamma _{0}\right) }\left(
        \sum_{u\in U} \epsilon(u)\;
        \dim \left( L_{\widetilde{\af_{\perp }}}^{\mu
        _{\widetilde{\af_{\perp }}}\left( u\right) }\right)
        \delta_{\xi-\gamma_0,\pi_{\af}(u(\mu+\rho)-\rho)}+ \right.\\
      \left.
        +\sum_{\gamma \in
          \Gamma _{\af \rightarrow \gf}}s\left( \gamma +\gamma _{0}\right) k_{\xi
          +\gamma }^{\left( \mu \right) }\right).
    \end{array}
  \end{equation}
\end{theorem}
\begin{proof}
Перепишем соотношение (\ref{eq:4}) для элемента $\frac{\Psi _{\gf}^{\mu }}{R_{\afb}}$ используя определение (\ref{eq:37})
для носителя $\Phi _{\af\subset \gf}$ ,
\begin{equation*}
\begin{array}{l}
\Psi ^{\left( \mu \right) }_{\left(  \af, \afb \right)}
=\pi _{\af}\left( \frac{\Psi _{\gf}^{\mu }}{R_{\af_{\perp }}}%
\right) = \\[2mm]
=\prod\limits_{\alpha \in \Delta ^{+}\setminus \Delta _{\afb }^{+}}\left(
1-e^{-\pi _{\af}\alpha }\right) ^{\mathrm{mult}(\alpha )-\mathrm{mult}_{%
\af}(\pi _{\af}\alpha )}\left( \sum\limits_{\nu \in P_{\af%
}^{+}}b_{\nu }^{(\mu )}\sum\limits_{w\in W_{\af}}\epsilon (w)e^{w(\nu
+\rho _{\af})-\rho _{\af}}\right) = \\[5mm]
=-\sum\limits_{\gamma \in \Phi _{\af\subset \gf}}s(\gamma
)e^{-\gamma }\left( \sum\limits_{\nu \in P_{\af}^{+},w\in W_{\af%
}}\epsilon (w)b_{\nu }^{(\mu )}e^{w(\nu +\rho _{\af})-\rho _{\af%
}}\right)  \\
=-\sum\limits_{\gamma \in \Phi _{\af\subset \gf}}s(\gamma
)e^{-\gamma }\left( \sum\limits_{\nu \in P_{\af}^{+},w\in W_{\af%
}}\epsilon (w)b_{\nu }^{(\mu )}e^{w(\nu +\rho _{\af})-\rho _{\af%
}}\right) .
\end{array}
\end{equation*}

Затем раскроем сумму в скобках (по отношению к формальному базису в  $\mathcal{E}$):
\begin{equation*}
\Psi ^{\left( \mu \right) }_{\left(  \af, \afb \right)}
=-\sum_{\gamma \in \Phi _{\af\subset \gf}}s(\gamma
)e^{-\gamma }\sum_{\lambda \in P_{\af}}k_{\nu }^{(\mu )}e^{\lambda
}=-\sum_{\gamma \in \Phi _{\af\subset \gf}}\sum_{\lambda \in P_{%
\af}}s(\gamma )k_{\nu }^{(\mu )}e^{\lambda -\gamma }.
\end{equation*}
Подставим выражение, полученное в Лемме \ref{lemma} (в левую часть),
\begin{eqnarray*}
\Psi ^{\left( \mu \right) }_{\left(  \af, \afb \right)}
&=&\sum_{u\in U}\;\epsilon (u)e^{\pi _{\af}\left( \mu _{\frak{a%
}}\left( u\right) \right) }\dim \left( L_{\widetilde{\af_{\perp }}%
}^{\mu _{\widetilde{\af_{\perp }}}\left( u\right) }\right)
\label{anom modules 2} \\
&=&\sum_{u\in U}\;\epsilon (u)e^{\pi _{\af}\left[ u(\mu +\rho )-\rho %
\right] }\dim \left( L_{\widetilde{\af_{\perp }}}^{\mu _{\widetilde{%
\af_{\perp }}}\left( u\right) }\right)  \\
&=&-\sum_{\gamma \in \Phi _{\af\subset \gf}}\sum_{\lambda \in P_{%
\af}}s(\gamma )k_{\nu }^{(\mu )}e^{\lambda -\gamma }.
\end{eqnarray*}
Из этого равенства немедленно следует
\begin{equation}
\sum_{u\in U}\epsilon (u)\dim \left( L_{\widetilde{\af_{\perp }}}^{\mu
_{\widetilde{\af_{\perp }}}\left( u\right) }\right) \delta _{\xi ,\pi _{%
\af}\left[ u(\mu +\rho )-\rho \right] }+\sum_{\gamma \in \Phi _{\af%
\subset \gf}}s(\gamma )\;k_{\xi +\gamma }^{(\mu )}=0,\quad \xi \in P_{%
\af}.  \label{eq:17}
\end{equation}
Полученная формула означает, что коэффициенты  $k_{\xi +\gamma }^{(\mu )}$ для  $\gamma \in \Phi _{\af\subset \gf}$ не независимы, а удовлетворяют линейным соотношениям. Вид этих соотношений меняется если тестовый вес  $\xi $ совпадает с одним из ``сингулярных весов''   $\left\{ \pi _{\af}\left[ u(\mu +\rho )-\rho \right] |u\in U\right\} $. В завершение доказательства мы вычитаем наименьший вес  $\gamma _{0}\in \Phi _{\af\subset \gf}$ и переходим к суммированию по векторам веера вложения $\Gamma _{\af\rightarrow \gf}$ (см. определение \ref{fan-definition}). Итак, мы получили искомое рекуррентное соотношение  (\ref{recurrent-relation}).
\end{proof}

\subsubsection{Вложения и ортогональные пары подалгебр простых алгебр Ли}
\label{sect-embeddings}
